ESRC SDAI Application

### 2019-05-18 Draft.tex
update

Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020. The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}. \textit{I found an \href{https://www.researchcatalogue.esrc.ac.uk/grants/ES.K002899.1/read}{SDAI Grant}  from 2014 in which they show that if the CSEW does not use capping when it comes to the number of reported DA incidents, the prevalence of DA against women increases between 2008 and 2014 (following a long decline), contrary to the overall decline in violent crimes. Shall I make a reference to this?}

@@

We first explore the characteristics of offenders and victims, focusing on gender, age and ethnicity.

Aim 1: Who perpetrates? Who becomes a victim? - our police dataset allows us to explore what other types of criminal behaviours abusers are likely to engage in/be a victim of; same for victims with police and CSEW; victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse? Find out what kind of cases get reported. Break down the 17\% based on socioeconomic and incident characteristics.

\subsection{Reporting behaviour}

@@

>>>>

Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020. The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}. These interventions are crucial in light of the fact that after a long decline, domestic violence against women has significantly increased between the period of 2008 and 2014 \textit{ref}.

@@

We first explore the characteristics of offenders and victims. \textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}

While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the offenders. Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are

The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services. We can validate and contrast these findings with insights from a spatial regression analysis of the crime data, using low-level geographical area information from the census.

Aim 1: Who perpetrates? Who becomes a victim? victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse? Find out what kind of cases get reported. Break down the 17\% based on socioeconomic and incident characteristics.

\subsection{Reporting behaviour and temporal dynamics}

@@

\newpage
